### 2023-01-16 doc/university-covid-firstsub.tex
more

University campuses present challenges to preventing SARS-CoV-2 transmission due to a high proportion of asymptomatic infections and high contact rates. SARS-CoV-2 outbreaks on the Princeton University campus offer an unusually well-documented perspective, rooted in mass asymptomatic testing, which was further informed by mathematical modeling approaches. Here, we test whether this model, which was previously used for guiding policy decisions, can capture the observed outbreak patterns on campus. Our analysis reveals strong coupling in epidemic dynamics on campus and in local communities.  Super-spreading events can drive transmission on campus, thereby weakening the dynamical coupling in campus and community outbreaks.

>>>>

University campuses present challenges to preventing SARS-CoV-2 transmission, due to a high proportion of asymptomatic infections and high contact rates. SARS-CoV-2 outbreaks on the Princeton University campus offer an unusually well-documented perspective, rooted in mass asymptomatic testing, further informed by mathematical modeling aimed at guiding policy decisions. Here, we show that this model can parsimoniously capture observed outbreak patterns on campus during different eras of control. Our analysis reveals that strong coupling between epidemic dynamics on campus and in local communities drives the early epidemic. Subsequently, especially in the omicron era, superspreading events came to dominate transmission on campus, thereby weakening the dynamical coupling of campus and community outbreaks.
